Assessing Tor's Usability as a Censorship Circumvention Tool

### 2015-05-12 cs261n-paper/paper.tex
Move screenshot to Resources, refer to it in the text.

\noindent If you would like to observe individual participants' cognitive walkthroughs, 
we transcribed the audio files from our experiment
and synced them to the screen capture we took during the duration of the experiment:
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \url{https://people.torproject.org/~dcf/uxsprint2015/}
\end{itemize}

>>>>

\noindent If you would like to observe individual participants' cognitive walkthroughs, 
we transcribed the audio files from our experiment
and synced them to the screen capture we took during the duration of the experiment.
Figure~\ref{walkthrough} shows a screenshot of one of the videos.
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \url{https://people.torproject.org/~dcf/uxsprint2015/}
\end{itemize}
